---
title: "Timothy Stephens <br> Curriculum vitae"
output:
  pagedown::html_paged:
    css: ["cv.css", "https://use.fontawesome.com/releases/v5.7.2/css/all.css"]
    number_sections: false
links-to-footnotes: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(knitr)
library(lubridate)
source("utility-functions.R")

#### publications #####
publications <- read_csv("../publications.csv") %>%
  mutate(date=paste(publication_date_year, publication_date_month, publication_date_day, sep='-')) %>%
  mutate(year = publication_date_year) %>%
  filter(include_in_full_cv == 'y') %>%
  arrange(-publication_date_year, -publication_date_month, -publication_date_day)

#### cv entries #####
cv_entries <- read_csv("../cv_entries.csv") %>% 
  filter(include_in_full_cv == 'y') %>%
  mutate(date_start=paste(date_start_year, date_start_month, date_start_day, sep='-')) %>%
  mutate(date_end=paste(date_end_year, date_end_month, date_end_day, sep='-')) %>%
  mutate(year_begin = date_start_year) %>%
  mutate(year_end = date_end_year) %>%
  mutate(year = ifelse((is.na(year_end) | year_begin == year_end),
                      year_begin,
                      str_c(year_begin, " --- ", year_end))) %>%
  mutate(across(2:4, as.numeric)) %>%
  arrange(-date_start_year, -date_start_month, -date_start_day)
```

<div class="grid-container"> 
<!-- top row -->
```{block type="grid-item", echo=TRUE}
## Personal summary {.summary}
I am a computational biologist working on understanding the forces that govern the interactions between organisms in ecologically critical environments, such as coral reefs, and the forces that drive major evolutionary transitions, such as the one that gave rise to the first photosynthetic Eukaryotas. I am also CTO of OceanOmics, a company dedicated to developing scalable tools for environmental health monitoring.
```

```{block type='grid-item', echo=TRUE}
## Contact information {.box}
<div class="info-box">

| left | Left |
|:-|:--------------------------------------------|
| <i class="fas fa-map-marker-alt"></i>|Department of Biochemistry and Microbiology, Rutgers University, USA|
| <i class="fa fa-envelope"></i> | ts942\@sebs.rutgers.edu |
| <i class="fas fa-globe"></i> | [timothystephens.github.io](https://timothystephens.github.io) |
| <i class="fab fa-github"></i> | [TimothyStephens](https://github.com/TimothyStephens) |
| <i class="fab fa-twitter"></i> | [\@timstep1383](https://mobile.twitter.com/timstep1383) |

</div>
```

</div>

## Education and Research Experience {.nohead .set-width-range}
```{r}
cv_entries %>% 
  filter(type == 'education' | what == 'Research Associate') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  select(year, what) %>% 
  kable()
```

## Awards and honours {.nohead .set-width-year}
```{r}
cv_entries %>% 
  filter(type == 'awards') %>% 
  mutate(what = str_c(what, ", ", where)) %>%  
  select(year_begin, what) %>% 
  manual_page_break_after_row("what", "Merit Scholarship for academic achievement") %>%
  kable()
```

## Publications {.nohead .set-width-year}
```{r}
publications %>%
  mutate(ref2print = str_c(authors_full, " ", title, ". *", journal, "*")) %>%
  mutate(ref2print = ifelse(!is.na(ref_info), 
                            str_c(ref2print, ", ", ref_info, ", ", year(date), "."), 
                            str_c(ref2print, ", ", year(date), "."))
         ) %>%
  mutate(ref2print = ifelse(!is.na(preprint), 
                            str_c(ref2print, " [[Preprint](", preprint, ")]"), 
                            ref2print)
         ) %>%
  mutate(ref2print = ifelse(!is.na(url), 
                            str_c(ref2print, " [[URL](", url, ")]"), 
                            ref2print)
         ) %>%
  mutate(ref2print = ifelse(!is.na(pdf), 
                            str_c(ref2print, " [[PDF](", pdf, ")]"), 
                            ref2print)
         ) %>%
  mutate(ref2print = ifelse(!is.na(additional_info), 
                            str_c(ref2print, " ", additional_info), 
                            ref2print)
         ) %>%
  select(year, ref2print) %>%
  manual_page_break_after_row("ref2print", "Algae obscura") %>%
  manual_page_break_after_row("ref2print", "encode tandemly repeated single-exon genes with adaptive functions") %>%
  knitr::kable()
```

## Grants {.nohead .set-width-year}
```{r}
cv_entries %>% 
  filter(type == 'minor_grants' | type == 'major_grants') %>% 
  mutate(what = if_else(!is.na(additional_info),
                        str_c(what, ", ", additional_info),
                        str_c(what))) %>% 
  select(year_begin, what) %>%
  manual_page_break_after_row("what", "Integrated genomic approaches to understand stress tolerance in bioethanol-producing yeasts and coral reef symbionts") %>%
  kable()
```

## Teaching experience {.nohead .set-width-range}
```{r}
cv_entries %>% 
  filter(type == 'teaching') %>% 
  mutate(what = ifelse(!is.na(additional_info), 
    str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where, "<br>", additional_info),
    str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where))) %>% 
  select(year, what) %>% 
#  manual_page_break_after_row("what", "Design and conducted lectures on de novo next-generation genome and") %>%
  kable()
```

## Professional development {.nohead .set-width-year}
```{r}
cv_entries %>% 
  filter(type == 'prof-dev') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  select(year_begin, what) %>% 
# manual_page_break_after_row("what", "UQ Idea Hub") %>%
  kable()
```

## Talks {.nohead .set-width-year}
```{r}
cv_entries %>% 
  filter(type == 'talk') %>% 
  select(year_begin, what) %>%
  manual_page_break_after_row("what", "Department of Molecular Biology and Biochemistry Seminar") %>%
  manual_page_break_after_row("what", "EMBL Australia Postgraduate Symposium") %>%
  kable()
```

## Poster presentations {.nohead .set-width-year}
```{r}
cv_entries %>% 
  filter(type == 'poster') %>%
  select(year_begin, what) %>%
#  manual_page_break_after_row("what", "The Extremophilic Red Algae That Underpin Hot Spring Microbial Communities In Yellowstone National Park") %>%
  kable()
```

## Media coverage {.nohead .set-width-year}
```{r}
cv_entries %>% 
  filter(type == 'media') %>%
  select(year_begin, what) %>% 
# manual_page_break_after_row("what", "Amoeba Genome Reveals Dominant Host Contribution to Plastid Endosymbiosis") %>%
  kable()
```

## Service {.nohead .set-width}
```{r}
cv_entries %>% 
  filter(type == 'service') %>% 
  mutate(year_end = ifelse(year_end == "present", "", year_end)) %>% 
  mutate(where = ifelse(!is.na(url), str_c("[", where, "](", url, ")"), where)) %>% 
  mutate(what = str_c(what, ", ", where)) %>%
  select(year, what) %>% 
#  manual_page_break_after_row("what", "Associate Editor: Symbiotic and Parasitic Protists section") %>%
  kable()
```

## Patents {.nohead .set-width}
```{r}
cv_entries %>%
  filter(type == 'patent') %>%
  mutate(what = ifelse(!is.na(additional_info), str_c(what, "<br>", additional_info), what)) %>%  
  select(year, what) %>% 
  kable()
```

```{r eval=FALSE}
## Reference letter writers {.nohead .set-width}
Prof. Debashish Bhattacharya (dbhattac@rutgers.edu)

Dr. Cheong Xin Chan (c.chan1@uq.edu.au)

Dr. Arthur Grossman (arthurg@stanford.edu)
```

```{r eval=FALSE}
## Personal skills & volunteering {.nohead .set-width}
cv_entries %>%
  filter(type == 'volunteering') %>%
  mutate(what = str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where)) %>%
  mutate(what = ifelse(!is.na(additional_info), str_c(what, "<br>", additional_info), what)) %>%
  select(year, what) %>%
  kable()
```
