---
title: "Timothy Stephens <br> Curriculum vitae"
output:
  pagedown::html_paged:
    css: ["cv.css", "https://use.fontawesome.com/releases/v5.7.2/css/all.css"]
    number_sections: false
links-to-footnotes: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(knitr)
library(lubridate)
source("utility-functions.R")

#### publications #####
publications <- read_csv("../publications.csv") %>%
  mutate(date=paste(publication_date_year, publication_date_month, publication_date_day, sep='-')) %>%
  mutate(year = publication_date_year) %>%
  filter(include_in_full_cv == 'y') %>%
  arrange(-publication_date_year, -publication_date_month, -publication_date_day)

#### cv entries #####
cv_entries <- read_csv("../cv_entries.csv") %>% 
  filter(include_in_full_cv == 'y') %>%
  mutate(date_start=paste(date_start_year, date_start_month, date_start_day, sep='-')) %>%
  mutate(date_end=paste(date_end_year, date_end_month, date_end_day, sep='-')) %>%
  mutate(year_begin = date_start_year) %>%
  mutate(year_end = date_end_year) %>%
  mutate(year = ifelse((is.na(year_end) | year_begin == year_end),
                      year_begin,
                      str_c(year_begin, " --- ", year_end))) %>%
  mutate(across(2:4, as.numeric)) %>%
  arrange(-date_start_year, -date_start_month, -date_start_day)
```

<div class="grid-container"> 
<!-- top row -->
```{block type="grid-item", echo=TRUE}
## Personal summary {.summary}
I am a computational biologist working on understanding the forces that govern the interactions between organisms in ecologically critical environments, such as coral reefs, and the forces that drive major evolutionary transitions, such as the one that gave rise to the first photosynthetic Eukaryotas.
```

```{block type='grid-item', echo=TRUE}
## Contact information {.box}
<div class="info-box">

| left | Left |
|:-|:--------------------------------------------|
| <i class="fas fa-map-marker-alt"></i>|Department of Biochemistry and Microbiology, Rutgers University, USA|
| <i class="fa fa-envelope"></i> | ts942\@sebs.rutgers.edu |
| <i class="fas fa-globe"></i> | [timothystephens.github.io](https://timothystephens.github.io) |
| <i class="fab fa-github"></i> | [TimothyStephens](https://github.com/TimothyStephens) |
| <i class="fab fa-twitter"></i> | [\@timstep1383](https://mobile.twitter.com/timstep1383) |

</div>
```

</div>

## Education {.nohead .set-width-range}
```{r}
cv_entries %>% 
  filter(type == 'education') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  select(year, what) %>% 
  kable()
```

## Research Experience {.nohead .set-width-range}
```{r}
cv_entries %>% 
  filter(type == 'research_experience') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  select(year, what) %>% 
  kable()
```

## Awards and honours {.nohead .set-width-year}
```{r}
cv_entries %>% 
  filter(type == 'awards') %>% 
  mutate(what = str_c(what, ", ", where)) %>%  
  select(year_begin, what) %>% 
  kable()
```

## Publications {.nohead .set-width-year}
```{r}
publications %>%
  mutate(ref2print = str_c(authors_full, " ", title, ". *", journal, "*")) %>%
  mutate(ref2print = ifelse(!is.na(ref_info), 
                            str_c(ref2print, ", ", ref_info, ", ", year(date), "."), 
                            str_c(ref2print, ", ", year(date), "."))
         ) %>%
  mutate(ref2print = ifelse(!is.na(preprint), 
                            str_c(ref2print, " [[Preprint](", preprint, ")]"), 
                            ref2print)
         ) %>%
  mutate(ref2print = ifelse(!is.na(url), 
                            str_c(ref2print, " [[URL](", url, ")]"), 
                            ref2print)
         ) %>%
  mutate(ref2print = ifelse(!is.na(pdf), 
                            str_c(ref2print, " [[PDF](", pdf, ")]"), 
                            ref2print)
         ) %>%
  mutate(ref2print = ifelse(!is.na(additional_info), 
                            str_c(ref2print, " ", additional_info), 
                            ref2print)
         ) %>%
  select(year, ref2print) %>%
  manual_page_break_after_row("ref2print", "Why is primary endosymbiosis so rare") %>%
  #manual_page_break_after_row("ref2print", "encode tandemly repeated single-exon genes with adaptive functions") %>%
  knitr::kable()
```

## Grants {.nohead .set-width-year}
```{r}
cv_entries %>% 
  filter(type == 'minor_grants' | type == 'major_grants') %>% 
  mutate(what = if_else(!is.na(additional_info),
                        str_c(what, ", ", additional_info, ", ", where),
                        str_c(what, ", ", where))) %>% 
  select(year_begin, what) %>% 
  kable()
```

## Teaching experience {.nohead .set-width-range}
```{r}
cv_entries %>% 
  filter(type == 'teaching') %>% 
  mutate(what = ifelse(!is.na(additional_info), 
    str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where, "<br>", additional_info),
    str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where))) %>% 
  select(year, what) %>% 
  kable()
```

## Professional development {.nohead .set-width-year}
```{r}
cv_entries %>% 
  filter(type == 'prof-dev') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  select(year_begin, what) %>% 
  kable()
```

## Talks {.nohead .set-width-year}
```{r}
cv_entries %>% 
  filter(type == 'talk') %>% 
  select(year_begin, what) %>%
  manual_page_break_after_row("what", "UQ Marine Ecogenomics Symposium 2023") %>%
  kable()
```

## Poster presentations {.nohead .set-width-year}
```{r}
cv_entries %>% 
  filter(type == 'poster') %>%
  select(year_begin, what) %>% 
  kable()
```

## Media coverage {.nohead .set-width-year}
```{r}
cv_entries %>% 
  filter(type == 'media') %>%
  select(year_begin, what) %>% 
  kable()
```

## Service {.nohead .set-width}
```{r}
cv_entries %>% 
  filter(type == 'service') %>% 
  mutate(year_end = ifelse(year_end == "present", "", year_end)) %>% 
  mutate(where = ifelse(!is.na(url), str_c("[", where, "](", url, ")"), where)) %>% 
  mutate(what = str_c(what, ", ", where)) %>%
  select(year, what) %>% 
  kable()
```

## Patents {.nohead .set-width}
```{r}
cv_entries %>%
  filter(type == 'patent') %>%
  mutate(what = ifelse(!is.na(additional_info), str_c(what, "<br>", additional_info), what)) %>%  
  select(year, what) %>% 
  kable()
```

```{r eval=FALSE}
## Reference letter writers {.nohead .set-width}
Prof. Debashish Bhattacharya (dbhattac@rutgers.edu)

Dr. Cheong Xin Chan (c.chan1@uq.edu.au)

Dr. Arthur Grossman (arthurg@stanford.edu)
```

```{r eval=FALSE}
## Personal skills & volunteering {.nohead .set-width}
cv_entries %>%
  filter(type == 'volunteering') %>%
  mutate(what = str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where)) %>%
  mutate(what = ifelse(!is.na(additional_info), str_c(what, "<br>", additional_info), what)) %>%
  select(year, what) %>%
  kable()
```
