---
title: "Timothy Stephens <br> Curriculum vitae"
output:
  pagedown::html_paged:
    css: ["cv.css", "https://use.fontawesome.com/releases/v5.7.2/css/all.css"]
    number_sections: false
links-to-footnotes: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(knitr)
library(lubridate)
source("utility-functions.R")

#### publications #####
publications <- read_csv("../publications.csv") %>%
  mutate(date=paste(publication_date_year, publication_date_month, publication_date_day, sep='-')) %>%
  mutate(year = publication_date_year) %>%
  filter(include_in_short_cv == 'y') %>%
  arrange(-publication_date_year, -publication_date_month, -publication_date_day)

#### cv entries #####
cv_entries <- read_csv("../cv_entries.csv") %>% 
  filter(include_in_short_cv == 'y') %>%
  mutate(date_start=paste(date_start_year, date_start_month, date_start_day, sep='-')) %>%
  mutate(date_end=paste(date_end_year, date_end_month, date_end_day, sep='-')) %>%
  mutate(year_begin = date_start_year) %>%
  mutate(year_end = date_end_year) %>%
  mutate(year = ifelse((is.na(year_end) | year_begin == year_end),
                      year_begin,
                      str_c(year_begin, " --- ", year_end))) %>%
  mutate(across(2:4, as.numeric)) %>%
  arrange(-date_start_year, -date_start_month, -date_start_day)
```

<div class="grid-container"> 
<!-- top row -->
```{block type="grid-item", echo=TRUE}
## Personal summary {.summary}
I am a computational biologist working on understanding and characterizing functionally uncharacterized "dark genes", which are found in all non-model genomes, but often ignored despite their immense biological importance. I am also CTO of OceanOmics, a company dedicated to developing scalable tools for environmental health monitoring.
```

```{block type='grid-item', echo=TRUE}
## Contact information {.box}
<div class="info-box">

| left | Left |
|:-|:--------------------------------------------|
| <i class="fas fa-map-marker-alt"></i>|Department of Biochemistry and Microbiology, Rutgers University, USA|
| <i class="fa fa-envelope"></i> | ts942\@sebs.rutgers.edu |
| <i class="fas fa-globe"></i> | [timothystephens.github.io](https://timothystephens.gitgub.io) |
| <i class="fab fa-github"></i> | [TimothyStephens](https://github.com/TimothyStephens) |
| <i class="fab fa-twitter"></i> | [\@timstep1383](https://mobile.twitter.com/timstep1383) |

</div>
```

</div>

## Education and Research Experience {.nohead .set-width-range}
```{r}
cv_entries %>% 
  filter(type == 'education' | what == 'Research Associate') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  mutate(year = str_c(year_begin, " --- ", year_end)) %>% 
  select(year, what) %>%
  kable()
```

## Selected Awards and honours {.nohead .set-width-year}
```{r}
cv_entries %>% 
  filter(type == 'awards') %>%
  mutate(what = str_c(what, ", ", where)) %>%  
  select(year_begin, what) %>%
  kable()
```

## Select Publications {.nohead .set-width-year}
```{r}
publications %>%
  mutate(ref2print = str_c(authors_full, " ", title, ". *", journal, "*")) %>%
  mutate(ref2print = ifelse(!is.na(ref_info), 
                            str_c(ref2print, ", ", ref_info, ", ", year(date), "."), 
                            str_c(ref2print, ", ", year(date), "."))
         ) %>%
  mutate(ref2print = ifelse(!is.na(preprint), 
                            str_c(ref2print, " [[Preprint](", preprint, ")]"), 
                            ref2print)
         ) %>%
  mutate(ref2print = ifelse(!is.na(additional_info), 
                            str_c(ref2print, " ", additional_info), 
                            ref2print)
         ) %>%
  mutate(ref2print = ifelse(!is.na(url), 
                            str_c(ref2print, " [[URL](", url, ")]"), 
                            ref2print)
         ) %>%
  mutate(ref2print = ifelse(!is.na(pdf), 
                            str_c(ref2print, " [[PDF](", pdf, ")]"), 
                            ref2print)
         ) %>%
  select(year, ref2print) %>%
  #manual_page_break_after_row("ref2print", "Ploidy variation and its") %>%
  #manual_page_break_after_row("ref2print", "Multi-omic characterization of the thermal stress phenome in the stony coral") %>%
  knitr::kable()
```

## Selected Grants {.nohead .set-width-year}
```{r}
cv_entries %>% 
  filter(type == 'minor_grants' | type == 'major_grants') %>% 
  mutate(what = if_else(!is.na(additional_info),
                        str_c(what, ", ", additional_info, ", ", where),
                        str_c(what, ", ", where))) %>% 
  select(year_begin, what) %>%
  manual_page_break_after_row("what", "Rutgers TechAdvance Fund") %>%
  kable()
```

## Selected Teaching experience {.nohead .set-width-range}
```{r}
cv_entries %>% 
  filter(type == 'teaching') %>% 
  mutate(what = ifelse(!is.na(additional_info), 
    str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where, "<br>", additional_info),
    str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where))) %>% 
  select(year, what) %>%
  #manual_page_break_after_row("what", "Co-lecturer") %>%
  kable()
```

## Selected Talks {.nohead .set-width-year}
```{r}
cv_entries %>% 
  filter(type == 'talk') %>% 
  select(year_begin, what) %>%
  #manual_page_break_after_row("what", "22-26th March 2021") %>%
  kable()
```

## Selected Media coverage {.nohead .set-width-year}
```{r}
cv_entries %>% 
  filter(type == 'media') %>%
  select(year_begin, what) %>% 
  kable()
```

## Selected Service {.service .nohead .set-width}
```{r}
cv_entries %>% 
  filter(type == 'service') %>% 
  mutate(year_end = ifelse(year_end == "present", "", year_end)) %>% 
  mutate(where = ifelse(!is.na(url), str_c("[", where, "](", url, ")"), where)) %>% 
  mutate(what = str_c(what, ", ", where)) %>%
  select(year, what) %>% 
  kable()
```

## Patents {.nohead .set-width}
```{r}
cv_entries %>%
  filter(type == 'patent') %>%
  #mutate(what = ifelse(!is.na(additional_info), str_c(what, "<br>", additional_info), what)) %>%  
  select(year, what) %>% 
  kable()
```

